Revisiting the hydrodynamic wave modulation from linear wave theory

### 2024-08-13 paper/paper.tex
Incorporate new analytical solution figures in the paper text

\begin{figure}[h]
\label{fig:wavenumber_modulation}
\centering
\includegraphics[width=\textwidth]{figures/fig_wavenumber_modulation_2panel.png}
\caption{
  Comparison of relative short-wave modulation as function of the
  long-wave phase, for a moderately steep long wave of $\varepsilon = 0.1$.
  The dotted line shows the 1st-order approximated solution by L-HS,
  the dashed line shows the exact solution by L-HS,
  and the solid line shows the extended solution introduced in this paper.
}
\end{figure}

@@

\begin{figure}[h]
\label{fig:gravity_modulation}
\centering
\includegraphics[width=\textwidth]{figures/fig_gravity_modulation_2panel.png}
\caption{
  Relative change in gravity of short waves due to a longer wave with steepness $a_L k_L = 0.2$,
  as a function of the long-wave phase and evaluated to the first (dashed line) and second (solid line) order in $a_L k_L$.
}
\end{figure}

@@

\begin{figure}[h]
\label{fig:frequency_modulation}
\centering
\includegraphics[width=\textwidth]{figures/fig_frequency_modulation_2panel.png}
\caption{
  (a) Relative change in the short-wave intrinsic frequency on the surface of a
  longer linear (black) and Stokes (red) wave of steepness $\varepsilon_L = 0.2$
  as function of long-wave phase;
  (b) Long-wave phase maximum (solid), mean (dashed), and minimum (dotted)
  relative change in the short-wave intrinsic frequency as function of long-wave
  steepness in the case of a linear (black) and Stokes (red) long wave.
}
\end{figure}

@@

\begin{figure}[h]
\label{fig:amplitude_modulation}
\centering
\includegraphics[width=\textwidth]{figures/fig_amplitude_modulation_2panel.png}
\caption{
}
\end{figure}

>>>>

\begin{figure}[ht]
\label{fig:analytical_solutions_ak0.1}
\centering
\includegraphics[width=0.8\textwidth]{figures/fig_analytical_solutions_ak0.1.png}
\caption{
}
\end{figure}

@@

@@

@@

\begin{figure}[ht]
\label{fig:analytical_solutions_ak0.2}
\centering
\includegraphics[width=0.8\textwidth]{figures/fig_analytical_solutions_ak0.2.png}
\caption{Same a Fig. \ref{fig:analytical_solutions_ak0.1} but for $\varepsilon_L = 0.2$.}
\end{figure}

\begin{figure}[ht]
\label{fig:analytical_solutions_ak0.4}
\centering
\includegraphics[width=0.8\textwidth]{figures/fig_analytical_solutions_ak0.4.png}
\caption{Same a Fig. \ref{fig:analytical_solutions_ak0.1} but for $\varepsilon_L = 0.4$.}
\end{figure}
